### 2019-12-20 article_draft.tex
Address some of Alex's comments

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(y^{(a)} = 1\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(y^{(a)}, w, a)
\end{align*}
The parameter of interest is $\beta_3^*$
\textcolor{blue}{The other $W_j$'s are included in the analysis and are marginalized over, but are not part of the defined model.} I am planning on using the same simulation settings as above, but also including non-changing effects for $a$, but am open to other ideas.
% \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
% In this setting, the outcome is \sh{some measure of health}, and the covariates correspond to genetic measurements $W_{ij}$ that take value one for \sh{genes or snips which dont match the reference genome} and zero for those that do match. It is of interest if the measured outcome is associated with these genetic measurements.

@@

Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm \textcolor{blue}{I don't understand the end of this sentence}.  However, this approach also works with more complicated functions.  Let $\Gamma_{\distv}(x)$ be a function that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$. \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}  The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
\textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both?}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

@@

\subsection{Obtaining the null distribution}
\label{ssec:obtaining_null}
The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.  To obtain an estimate of this limiting distribution, assume the vector of parameter estimates $\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized. Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.  That is for each $j \in \{1, \dots, d\}$:
\begin{align*}
\hat{\psi}_j = \psi_j + \frac{1}{n}\sum_{i=1}^n D_j(\boldsymbol{x}_i) + o_p(1/\sqrt{n}) \text{ for some function } D_j
\end{align*}
When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$: \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$? This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}

>>>>

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
\end{align*}
The parameter of interest is $\beta_3^*$
\textcolor{blue}{The other $W_j$'s are included in the analysis and are marginalized over, but are not part of the defined model.} I am planning on using the same simulation settings as above, but also including non-changing effects for $a$, but am open to other ideas.
% \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
% In this setting, the outcome is \sh{some measure of health}, and the covariates correspond to genetic measurements $W_{ij}$ that take value one for \sh{genes or snips which dont match the reference genome} and zero for those that do match. It is of interest if the measured outcome is associated with these genetic measurements.

@@

Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
Above, we have used a single norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$ which allows for creating tests and calculating p-values similar to the univariate case. 
% \textcolor{blue}{I don't understand the end of this sentence}.
However, this approach also works with more complicated functions.  For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
\textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both?}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

@@

\subsection{Obtaining the null distribution}
\label{ssec:obtaining_null}
The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.  To obtain an estimate of this limiting distribution, assume the vector of parameter estimates $\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized. Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.  That is for each $j \in \{1, \dots, d\}$:
\begin{align*}
\hat{\psi}_j = \psi_j + \frac{1}{n}\sum_{i=1}^n D_j(\boldsymbol{x}_i) + o_p(1/\sqrt{n}) \text{ for some function } D_j
\end{align*}
When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
%  \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$? This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}
